### 2024-12-03 paper/sections/abstract.tex
paper: add template

\documentclass[../main.tex]{subfiles}
\begin{document}
Your abstract text goes here. Just a few facts. Whet our appetites.
Not more than 200 words, if possible, and preferably closer to 150.
\end{document}

### 2024-12-03 paper/sections/introduction.tex
paper: add template

\documentclass[../main.tex]{subfiles}
\begin{document}
A paragraph of text goes here. Lots of text. Plenty of interesting
text. Text text text text text text text text text text text text text
text text text text text text text text text text text text text text
text text text text text text text text text text text text text text
text text text text text text text.
More fascinating text. Features galore, plethora of promises.
\end{document}

### 2024-12-05 ebpfccp/src/datapath.rs
feat(ebpfccp): remove logging

@@ -165,7 +165,6 @@ impl Skeleton {
         thread::spawn(move || loop {
             match rx.recv() {
                 Ok(ConnectionMessage::SetCwnd(sock_addr, cwnd)) => {
-                    println!("Setting cwnd for {:?} to {}", sock_addr, cwnd);
                     if let Err(e) = update_connection(skel, sock_addr, |conn| {
                         conn.cwnd = cwnd;
                     }) {
@@ -173,7 +172,6 @@ impl Skeleton {
                     }
                 }
                 Ok(ConnectionMessage::SetRateAbs(sock_addr, rate)) => {
-                    println!("Setting pacing rate for {:?} to {}", sock_addr, rate);
                     if let Err(e) = update_connection(skel, sock_addr, |conn| {
                         conn.pacing_rate = rate;
                     }) {

### 2024-12-05 ebpfccp/src/manager.rs

@@ -191,7 +191,6 @@ impl Manager {
         let tx = skeleton.sender();
         skeleton.poll_create_conn_events(move |event| {
             // A new flow has been created: create a new connection and store it
-            println!("Received create connection event");
 
             // Create a new connection
             let conn = Connection::new(event.sock_addr, tx.clone());
@@ -211,7 +210,6 @@ impl Manager {
         let connections = self.connections.clone();
         skeleton.poll_free_conn_events(move |event| {
             // A connection has been freed: remove it from the map
-            println!("Received free connection event");
             let mut connections = connections.write().unwrap();
             connections.remove(&event.sock_addr);
         })

### 2024-12-06 benchmark/gen_graph.py
chore: removed prints

@@ -13,8 +13,8 @@ total_seconds = 30            # total time to run iperf3
 report_interval = 0.1         # report interval for iperf3
 ccas = ["cubic", "bpf_cubic", "ebpfccp", "ccp"] # list of CCAs to benchmark, must all be registered
 trials = 10                   # amount of trials to average performance over
-y_unit = "bytes"              
-use_sum = True
+y_unit = "bits_per_second"              
+use_sum = False
 # End of user-defined options
                 
 
@@ -77,6 +77,7 @@ else:
     perf_results = {}
     for cca in ccas:
         # process each json file for each cca
+        print(cca)
         cca_xs = []
         cca_ys = []
         total_cpu_perf = 0
@@ -104,19 +105,12 @@ else:
                 print(f"Invalid value in {cpu_perf_file}")
                 continue
         max_len = len(max(cca_xs, key=len))
-        print(max_len)
         def pad_length(arr: NDArray) -> NDArray:
             after = np.pad(arr, (0, max_len - len(arr)), constant_values=arr[-1])
-            print(f"Before: {arr.shape}, after: {after.shape}")
             return after
         cca_xs = np.array(list(map(pad_length, cca_xs)))
         cca_ys = np.array(list(map(pad_length, cca_ys)))
         average_xs = np.mean(cca_xs, axis=0)
-        prev = 0
-        for x in average_xs:
-            if x < prev:
-                print(f"Decrease detected: prev: {prev}, curr: {x}")
-            prev = x
         average_ys = np.mean(cca_ys, axis=0)
         results.append(Result(average_xs, average_ys, cca))
         perf_results[cca] = total_cpu_perf / trials

### 2024-12-06 benchmark/benchmark.sh
feat: switched performance to box-and-whiskers graph

@@ -20,5 +20,4 @@ iperf3 -c $TARGET_SERVER -p $TARGET_PORT \
 --json --verbose --timestamps --interval $REPORT_INTERVAL \
 --time $TOTAL_SECONDS --logfile "${CCA}_${TRIAL}.json"
 
-echo "Trial $TRIAL for $CCA done, sleeping for 5 seconds"
-sleep 5
+echo "Trial $TRIAL for $CCA done"

### 2024-12-06 benchmark/gen_graph.py

@@ -1,6 +1,7 @@
 import matplotlib.pyplot as plt
 import json
 import os
+import time
 import numpy as np
 import numpy.typing as npt
 NDArray = npt.NDArray[np.float64]
@@ -9,7 +10,7 @@ NDArray = npt.NDArray[np.float64]
 # User-defined options
 target_server = "bokaibi.com" # server running iperf3 in server mode
 target_port = 5142            # iperf3 server port
-total_seconds = 30            # total time to run iperf3
+total_seconds = 15            # total time to run iperf3
 report_interval = 0.1         # report interval for iperf3
 ccas = ["cubic", "bpf_cubic", "ebpfccp", "ccp"] # list of CCAs to benchmark, must all be registered
 trials = 10                   # amount of trials to average performance over
@@ -66,21 +67,22 @@ if mode == "1":
     # run benchmark
     print("Running the benchmark for the following CCAs: ", ccas)
     print(f"Parameters: target_server={target_server}, target_port={target_port}, total_seconds={total_seconds}, report_interval={report_interval}, trials={trials}")
-    default_waittime = 5
-    print(f"Expected run time: {trials * (total_seconds + default_waittime) * len(ccas)}")
+    default_waittime = 0.5
+    print(f"Expected run time: {trials * (total_seconds + default_waittime) * len(ccas)} seconds")
     for t in range(trials):
         for cca in ccas:
             os.system(f"sudo bash benchmark.sh {target_server} {target_port} {total_seconds} {report_interval} {cca} {t+1}")
+            time.sleep(default_waittime)
 else:
     print(f"Data processing options: y_unit={y_unit}, use_sum={use_sum}")
     results = []
     perf_results = {}
+    max_perf = 0
     for cca in ccas:
         # process each json file for each cca
-        print(cca)
         cca_xs = []
         cca_ys = []
-        total_cpu_perf = 0
+        all_cpu_perf = []
         for trial in range(1, trials+1):
             file = os.path.join(os.getcwd(), f"{cca}_{trial}.json")
             try:
@@ -97,7 +99,8 @@ else:
             try:
                 with open(cpu_perf_file, "r") as f:
                     cpu_perf = int(f.read())
-                    total_cpu_perf += cpu_perf
+                    all_cpu_perf.append(cpu_perf)
+                    max_perf = max(max_perf, cpu_perf)
             except FileNotFoundError:
[…]

### 2024-12-06 benchmark/gen_graph.py
chore: increased default trial size

@@ -13,7 +13,7 @@ target_port = 5142            # iperf3 server port
 total_seconds = 15            # total time to run iperf3
 report_interval = 0.1         # report interval for iperf3
 ccas = ["cubic", "bpf_cubic", "ebpfccp", "ccp"] # list of CCAs to benchmark, must all be registered
-trials = 10                   # amount of trials to average performance over
+trials = 20                   # amount of trials to average performance over
 y_unit = "bits_per_second"              
 use_sum = False
 # End of user-defined options

### 2024-12-06 paper/sections/abstract.tex
feat: completed abstract & introduction, started on related works and mostly finished on eval

@@
 \begin{document}
-Your abstract text goes here. Just a few facts. Whet our appetites.
-Not more than 200 words, if possible, and preferably closer to 150.
+Implementing new CCAs (congestion control algorithms) is traditionally a time-consuming and error-prone process.
+Developing new CCAs directly in the kernel not only requires the developer to have advanced knowledge about kernel programming, but also still introduces opportunities for potentially fatal bugs that will crash the kernel.
+Furthermore, the development and testing process is made slow from the constant need to reboot and difficulties in running.
+While developing CCAs as kernel modules (https://pbg.cs.illinois.edu/papers/jay18pcc-kernel.pdf) has traditionally been an accepted alternative, running developmental software directly in the kernel still introduces instability and crashes.
+Recent research, such as CCP (CCP), explored the possibility of developing and running CCAs in userspace, having the algorithm communicate with the kernel through a developer-friendly datapath api that is vetted for safety.
+Simultaneously, developing CCAs in eBPF (https://dl.acm.org/doi/10.1145/3609021.3609295) has been explored as a new alternative as the eBPF verifier checks the provided program for issues like memory-safety violations and infinite loops.
+In this paper, we will evaluate the different approaches to CCA development by measuring their behavioral correctness and performance cost.
 \end{document}

### 2024-12-06 paper/sections/evaluation.tex
paper: add template
feat: completed abstract & introduction, started on related works and mostly finished on eval

--- 2024-12-03 paper/sections/abstract.tex
@@
 \begin{document}
-Your abstract text goes here. Just a few facts. Whet our appetites.
-Not more than 200 words, if possible, and preferably closer to 150.
+We included two sets of benchmarks: a behavioral benchmark aimed to verify the "correctness" of different implementations (TCP Cubic should behave similarly no matter where it is implemented, as indicated by metrics such as bitrate/congestion window size over time), and a performance benchmark aimed to measure the CPU overhead of different implementation approaches.
+A CCA implementation with smaller CPU overhead would logically lead to a higher maximum bandwidth in an ideal, infinite-speed connection where the CPU running the CCA is the bottleneck.
+\\
+Our benchmarks are ran with iperf3 (cite).
+For each trial, we loop through every CCA we are testing and run iperf3 for 15 seconds.
+At the same time, we run a Python script that loops infinitely and adds 1 to an accumulator at every loop.
+Once the 15 seconds are up, the script then outputs the final number into a file, a higher number suggesting that the script was able to access more CPU cycles.
+We run 20 trials to ensure statistical reliability.
+\\
+After all the trials, we average the behavioral metric across the trials and plot the average for each CCA through time as the behavioral benchmark.
+We then plot the CPU performances for each CCA across trials on a boxplot.
+In order to make sure we are correctly benchmarking the performance impact of CCAs instead of confounding factors, we ran the benchmark on an out-of-the-box Debian images on a VM.
+To ensure the CPU benchmark and the CCA are running on the same CPU, our VM is set up to contain only one core.
+[Results and interpretations]
 \end{document}

### 2024-12-06 paper/sections/introduction.tex
feat: completed abstract & introduction, started on related works and mostly finished on eval

@@
 \begin{document}
-A paragraph of text goes here. Lots of text. Plenty of interesting
-text. Text text text text text text text text text text text text text
-text text text text text text text text text text text text text text
-text text text text text text text text text text text text text text
-text text text text text text text.
-More fascinating text. Features galore, plethora of promises.
+Congestion Control Algorithms form a critical part of the Internet ecosystem.
+While traditional discussions about CCAs centered around ideas like fairness between users (cite flow-based fairness/tcp friendly paper here), newer research explored potentials for CCAs to improve network performance (cite BBR?) and allow the user to customize bandwidth allocated to different applications on the same machine.
+Research on various old and new congestion control algorithms is critical to the stable operation and continuous improvement of the Internet.
+\\
+The development of new CCAs faced two problems.
+The first problem being the high friction of development: CCAs have traditionally ran inside the networking stack in the kernel.
+As a result, developer of new CCAs are required to program in a kernel environment, forming a high barrier of entry and enabling potential high-impact bugs.
+The second problem being the difficulties of distribution.
+Though some have argued for abolishing the idea of flow-based fairness (Dismantling), TCP-Friendliness has nevertheless remained a central piece for any CCA-related research.
+To correctly evaluated the impacts of a new CCA on the Internet ecosystem, we need to be able to see significant real-world adoption from actual users around the world.
+Pushing a new, untested CCA upstream to the Linux kernel is an extremely difficult, if not outright impossible task.
+As a result, any CCA wishing to see eventual large-scale adoption must first propose a relatively user-friendly way for people to adopt it in the early stages.
+\\
+We believe that eBPF as a platform for implementing congestion control solves both problems.
+On the friction side, while programming in eBPF still requires a non-negligible amount of domain expertise, the process is nevertheless much simpler when compared to developing kernel modules, for example.
+The runtime-attached nature of eBPF makes iterating and testing new versions much easier.
+Furthermore, the eBPF VM and Verifier provide powerful guarantees to the safety of the program, protecting against large amounts of hard-to-solve bugs that lead to the kernel crashing.
+On the adoption side, the safety guarantees provided by eBPF will greatly encourage user adoption.
+While users can be hesitant in installing kernel patches or modules, attaching a eBPF program is much lower-risk and appealing if the new CCA itself promises significant improvements.\\
+Despite these upsides, running CCAs in eBPF can possibly incur extra costs due to running in the eBPF VM.
+By instrumenting the performance overheads of various different ways of implementing CCAs, we would like to explore whether eBPF is a viable long-term platform to implement CCAs on, or would researchers be better-off to switch to a kernel space implementation once a proof-of-concept was done on eBPF.
+In addition to CCAs directly implemented in eBPF, we also tested other means of developing CCAs quickly and safely.
+The Congestion Control Plane (CCP) (cite CCP) is an idea proposed to implement CCAs in user space.
+Since the original CCP kernel datapath is written as a Linux kernel module, we also implemented an alternative datapath in eBPF to potentially take advantage of the safety guarantees.
 \end{document}

### 2024-12-06 paper/sections/relatedwork.tex
paper: add template
feat: completed abstract & introduction, started on related works and mostly finished on eval

--- 2024-12-03 paper/sections/introduction.tex
@@
 \begin{document}
-A paragraph of text goes here. Lots of text. Plenty of interesting
-text. Text text text text text text text text text text text text text
-text text text text text text text text text text text text text text
-text text text text text text text text text text text text text text
-text text text text text text text.
-More fascinating text. Features galore, plethora of promises.
+CCP decoupled data gathering and CCA computation.
+A datapath module gathers information regarding a TCP flow and sends it to user space via various methods (such as netlink sockets and unix pipes), while a user space program listens to the given data and sends back any updates to be made to the TCP connection state.
+Platform/OS independence
 \end{document}

### 2024-12-06 paper/sections/abstract.tex
paper: reword abstract

--- 2024-12-03 paper/sections/abstract.tex
@@
 \begin{document}
-Your abstract text goes here. Just a few facts. Whet our appetites.
-Not more than 200 words, if possible, and preferably closer to 150.
+Developing new Congestion Control Algorithms (CCAs) has traditionally been a time-consuming and error-prone process.
+Creating these algorithms directly within the Linux kernel demands a high level of kernel programming expertise while still leaving room for bugs that can crash the system.
+Although implementing CCAs as kernel modules has traditionally been an accepted alternative (https://pbg.cs.illinois.edu/papers/jay18pcc-kernel.pdf), it still runs the risk of introducing instability and crashes.
+Recent research has implemented a Congestion Control Plane (CCP) (https://akshayn.xyz/res/ccp-sigcomm18.pdf) that allows CCA developers to implement CCAs in userspace, eliminating the need to run experimental software directly in the kernel.
+This approach involves a carefully designed and safety-checked datapath API; however, the Linux kernel datapath API still relies on a kernel module.
+Simultaneously, developing CCAs in eBPF (https://dl.acm.org/doi/10.1145/3609021.3609295) has emerged as another promising approach, leveraging the eBPF verifier to ensure safety before the code ever runs in the kernel.
+In this paper, we compare these various approaches -- kernel-based, eBPF-based, and userspace (via CCP) -- along with a new hybrid userspace eBPF-based approach (ebpfccp) for behavioral correctness and performance overhead.
 \end{document}

### 2024-12-06 paper/sections/design.tex
paper: add template
feat: Finished intro, related work, and evaluation templates; started on design; refused to use paper: as a commit tag

--- 2024-12-03 paper/sections/abstract.tex
@@
 \begin{document}
-Your abstract text goes here. Just a few facts. Whet our appetites.
-Not more than 200 words, if possible, and preferably closer to 150.
+We believe that an alternative implementation of an existing CCA can be evaluated using two metrics.
+First, whether or not the behavior of the implementation matches (to a reasonable extent) existing implementations of the same CCA.
+Secondly, the performance costs of the implementation when compared to other implementations.
+We included two sets of benchmarks to measure this: a behavioral benchmark aimed to verify the "correctness" of different implementations (TCP Cubic should behave similarly no matter where it is implemented, as indicated by metrics such as bitrate/congestion window size over time), and a performance benchmark aimed to measure the CPU overhead of different implementation approaches.
+A CCA implementation with smaller CPU overhead would logically lead to a higher maximum bandwidth in an ideal, infinite-speed connection where the CPU running the CCA is the bottleneck.
+\\
+Our benchmarks are ran with iperf3 (cite).
+For each trial, we loop through every CCA we are testing and run iperf3 for 15 seconds.
+At the same time, we run a Python script that loops infinitely and adds 1 to an accumulator at every loop.
+Once the 15 seconds are up, the script then outputs the final number into a file, a higher number suggesting that the script was able to access more CPU cycles.
+We ran 20 trials to ensure statistical reliability.
+Our testing script also included various parameters that can be tuned, including trial duration, reporting intervals, and the metric to be used while generating graphs for the behavioral benchmark.
+\\
+After all the trials, we average the behavioral metric across the trials and plot the average for each CCA through time as the behavioral benchmark.
+We then plot the CPU performances for each CCA across trials on a boxplot.
+\\
+
 \end{document}

### 2024-12-07 paper/main.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Template for USENIX papers.
%
% History:
%
% - TEMPLATE for Usenix papers, specifically to meet requirements of
%   USENIX '05. originally a template for producing IEEE-format
%   articles using LaTeX. written by Matthew Ward, CS Department,
%   Worcester Polytechnic Institute. adapted by David Beazley for his
%   excellent SWIG paper in Proceedings, Tcl 96. turned into a
%   smartass generic template by De Clarke, with thanks to both the
%   above pioneers. Use at your own risk. Complaints to /dev/null.
%   Make it two column with no page numbering, default is 10 point.
%
% - Munged by Fred Douglis <douglis@research.att.com> 10/97 to
%   separate the .sty file from the LaTeX source template, so that
%   people can more easily include the .sty file into an existing
%   document. Also changed to more closely follow the style guidelines
%   as represented by the Word sample file.
%
% - Note that since 2010, USENIX does not require endnotes. If you
%   want foot of page notes, don't include the endnotes package in the
%   usepackage command, below.
% - This version uses the latex2e styles, not the very ancient 2.09
%   stuff.
%
% - Updated July 2018: Text block size changed from 6.5" to 7"
%
% - Updated Dec 2018 for ATC'19:
%
%   * Revised text to pass HotCRP's auto-formatting check, with
%     hotcrp.settings.submission_form.body_font_size=10pt, and
%     hotcrp.settings.submission_form.line_height=12pt
%
%   * Switched from \endnote-s to \footnote-s to match Usenix's policy.
%
%   * \section* => \begin{abstract} ... \end{abstract}
%
%   * Make template self-contained in terms of bibtex entires, to allow
%     this file to be compiled. (And changing refs style to 'plain'.)
%
%   * Make template self-contained in terms of figures, to
%     allow this file to be compiled. 
%
%   * Added packages for hyperref, embedding fonts, and improving
%     appearance.
%   
%   * Removed outdated text.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix-2020-09}
\usepackage{subfiles}

% to be able to draw some self-contained figs
\usepackage{tikz}
\usepackage{amsmath}

% inlined bib file
\usepackage{filecontents}

%-------------------------------------------------------------------------------
\begin{filecontents}{\jobname.bib}
%-------------------------------------------------------------------------------
@Book{arpachiDusseau18:osbook,
  author =       {Arpaci-Dusseau, Remzi H. and Arpaci-Dusseau Andrea C.},
  title =        {Operating Systems: Three Easy Pieces},
  publisher =    {Arpaci-Dusseau Books, LLC},
  year =         2015,
  edition =      {1.00},
  note =         {\url{http://pages.cs.wisc.edu/~remzi/OSTEP/}}
}
@InProceedings{waldspurger02,
  author =       {Waldspurger, Carl A.},
  title =        {Memory resource management in {VMware ESX} server},
  booktitle =    {USENIX Symposium on Operating System Design and
                  Implementation (OSDI)},
  year =         2002,
  pages =        {181--194},
  note =         {\url{https://www.usenix.org/legacy/event/osdi02/tech/waldspurger/waldspurger.pdf}}}
\end{filecontents}

%-------------------------------------------------------------------------------
\begin{document}
%-------------------------------------------------------------------------------

%don't want date printed
\date{}

% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Evaluating eBPF as a Platform for Congestion Control Algorithm}

%for single author (just remove % characters)
\author{
{\rm Edward Wibowo}\\
Brown University
\and
{\rm Bokai Bi}\\
Brown University
% copy the following lines to add more authors
% \and
% {\rm Name}\\
%Name Institution
} % end author

\maketitle

%-------------------------------------------------------------------------------
\begin{abstract}
%-------------------------------------------------------------------------------
\subfile{sections/abstract}
\end{abstract}

%-------------------------------------------------------------------------------
\section{Introduction}
%-------------------------------------------------------------------------------
\subfile{sections/introduction}

%-------------------------------------------------------------------------------
\section{Related Work}
%-------------------------------------------------------------------------------
\subfile{sections/relatedwork}

%-------------------------------------------------------------------------------
\section{Design Overview}
%-------------------------------------------------------------------------------
\subfile{sections/design}

%-------------------------------------------------------------------------------
\section{Evaluation}
%-------------------------------------------------------------------------------
\subfile{sections/evaluation}

%-------------------------------------------------------------------------------
\section{Limitations}
%-------------------------------------------------------------------------------
\subfile{sections/limitations}

%-------------------------------------------------------------------------------
\section{Conclusion}
%-------------------------------------------------------------------------------
\subfile{sections/conclusion}

%% ANYTHING BELOW HERE IS FROM THE ORIGINAL TEMPLATE, SHOULD BE REMOVED LATER

%-------------------------------------------------------------------------------
\section{Footnotes, Verbatim, and Citations}
%-------------------------------------------------------------------------------

Footnotes should be places after punctuation characters, without any
spaces between said characters and footnotes, like so.%
\footnote{Remember that USENIX format stopped using endnotes and is
  now using regular footnotes.} And some embedded literal code may
look as follows.

\begin{verbatim}
int main(int argc, char *argv[]) 
{
    return 0;
}
\end{verbatim}

Now we're going to cite somebody. Watch for the cite tag. Here it
comes. Arpachi-Dusseau and Arpachi-Dusseau co-authored an excellent OS
book, which is also really funny~\cite{arpachiDusseau18:osbook}, and
Waldspurger got into the SIGOPS hall-of-fame due to his seminal paper
about resource management in the ESX hypervisor~\cite{waldspurger02}.

The tilde character (\~{}) in the tex source means a non-breaking
space. This way, your reference will always be attached to the word
that preceded it, instead of going to the next line.

And the 'cite' package sorts your citations by their numerical order
of the corresponding references at the end of the paper, ridding you
from the need to notice that, e.g, ``Waldspurger'' appears after
``Arpachi-Dusseau'' when sorting references
alphabetically~\cite{waldspurger02,arpachiDusseau18:osbook}.

It'd be nice and thoughtful of you to include a suitable link in each
and every bibtex entry that you use in your submission, to allow
reviewers (and other readers) to easily get to the cited work, as is
done in all entries found in the References section of this document.

Now we're going take a look at Section~\ref{sec:figs}, but not before
observing that refs to sections and citations and such are colored and
clickable in the PDF because of the packages we've included.

%-------------------------------------------------------------------------------
\section{Floating Figures and Lists}
\label{sec:figs}
%-------------------------------------------------------------------------------

%---------------------------
\begin{figure}
\begin{center}
\begin{tikzpicture}
  \draw[thin,gray!40] (-2,-2) grid (2,2);
  \draw[<->] (-2,0)--(2,0) node[right]{$x$};
  \draw[<->] (0,-2)--(0,2) node[above]{$y$};
  \draw[line width=2pt,blue,-stealth](0,0)--(1,1)
        node[anchor=south west]{$\boldsymbol{u}$};
  \draw[line width=2pt,red,-stealth](0,0)--(-1,-1)
        node[anchor=north east]{$\boldsymbol{-u}$};
\end{tikzpicture}
\end{center}
\caption{\label{fig:vectors} Text size inside figure should be as big as
  caption's text. Text size inside figure should be as big as
  caption's text. Text size inside figure should be as big as
  caption's text. Text size inside figure should be as big as
  caption's text. Text size inside figure should be as big as
  caption's text. }
\end{figure}
%% %---------------------------

Here's a typical reference to a floating figure:
Figure~\ref{fig:vectors}. Floats should usually be placed where latex
wants then. Figure\ref{fig:vectors} is centered, and has a caption
that instructs you to make sure that the size of the text within the
figures that you use is as big as (or bigger than) the size of the
text in the caption of the figures. Please do. Really.

In our case, we've explicitly drawn the figure inlined in latex, to
allow this tex file to cleanly compile. But usually, your figures will
reside in some file.pdf, and you'd include them in your document
with, say, \textbackslash{}includegraphics.

Lists are sometimes quite handy. If you want to itemize things, feel
free:

\begin{description}

\item[fread] a function that reads from a \texttt{stream} into the
  array \texttt{ptr} at most \texttt{nobj} objects of size
  \texttt{size}, returning returns the number of objects read.

\item[Fred] a person's name, e.g., there once was a dude named Fred
  who separated usenix.sty from this file to allow for easy
  inclusion.
\end{description}

\noindent
The noindent at the start of this paragraph in its tex version makes
it clear that it's a continuation of the preceding paragraph, as
opposed to a new paragraph in its own right.

\subsection{LaTeX-ing Your TeX File}
%-----------------------------------

People often use \texttt{pdflatex} these days for creating pdf-s from
tex files via the shell. And \texttt{bibtex}, of course. Works for us.

%-------------------------------------------------------------------------------
\section*{Acknowledgments}
%-------------------------------------------------------------------------------

The USENIX latex style is old and very tired, which is why
there's no \textbackslash{}acks command for you to use when
acknowledging. Sorry.

%-------------------------------------------------------------------------------
\section*{Availability}
%-------------------------------------------------------------------------------

USENIX program committees give extra points to submissions that are
backed by artifacts that are publicly available. If you made your code
or data available, it's worth mentioning this fact in a dedicated
section.

%-------------------------------------------------------------------------------
\bibliographystyle{plain}
\bibliography{\jobname}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%  LocalWords:  endnotes includegraphics fread ptr nobj noindent
%%  LocalWords:  pdflatex acks

### 2024-12-07 paper/sections/evaluation.tex

--- 2024-12-03 paper/sections/abstract.tex
@@
 \begin{document}
-Your abstract text goes here. Just a few facts. Whet our appetites.
-Not more than 200 words, if possible, and preferably closer to 150.
+In order to make sure we are correctly benchmarking the performance impact of CCAs rather than miscellneous confounding factors, we ran the benchmark on an out-of-the-box Debian image on a VM.
+To ensure the CPU benchmark and the CCA are running on the same CPU, our VM is set up to contain only one core.
+We also decided to run our benchmarks on various implementations of TCP Cubic due to its wide availability across platforms.
+\\
+The results of behavioral benchmarks are shown in Figure \ref{fig:behavioral}.
+From the graph, we can see that [to-be-added-conclusion].
+The results of CPU benchmarks are shown in Figure \ref{fig:cpu}.
+The eBPF implementation of TCP Cubic achieved impressive CPU performance compared to the built-in Linux kernel networking stack implementation.
+CCP-Cubic from the CCP Project (cite generic-cong-avoid git repo) combined with the kernel module + netlink CCP datapath achieved slightly lower performance, where its median is at x percent of the full kernel implementation value.
+Our implementation of eBPFCCP ranked lower on the performance chart, but was still able to achieve y percent of the full kernel implementation value.
+Due to the relative comparability of CPU performance between the kernel and eBPF implementations of TCP Cubicm, we theorize the noticable gap between eBPFCCP and kernel module CCP was due to our choice of using unix pipes rather than netlink as a channel for communicating between the eBPFCCP and the user space program.
+\\
+From these results, we can conclude that eBPF is a viable platform for the development CCAs.
+The negligible performance overhead when compared to the kernel native implementation is impressive, and suggests that eBPF-CCAs can possibly also be used as a long-term deployment option outside of research and development stages.
 \end{document}

### 2024-12-07 paper/sections/relatedwork.tex

@@
 \begin{document}
-CCP decoupled data gathering and CCA computation.
-A datapath module gathers information regarding a TCP flow and sends it to user space via various methods (such as netlink sockets and unix pipes), while a user space program listens to the given data and sends back any updates to be made to the TCP connection state.
-Platform/OS independence
+In order to fully evaluate performance of eBPF-based CCAs against alternative approaches, we looked at prior research aimed at reducing CCA-development overhead.
+Specifically, the Congestion Control Plane was developed to be an abstraction layer where developers can experiment with new CCA ideas without worrying about the intricacies of kernel networking stacks.
+Most notably, CCP decoupled data gathering and CCA computation.
+A datapath module gathers information regarding a TCP flow and sends it to user space via various channels, such as netlink sockets and unix pipes.
+A user space program then listens to the provided data and sends back any updates to be made to the TCP connection state.
+Since the computation lives in user space, developers are shielded from the potential of introducing kernel-crashing bugs as long as the underlying CCP datapath implementation is safe.
+The separation of data-gathering and computation also allows for further platform/OS independence.
+While traditional CCAs are tightly coupled with the kernel networking stack they are developed on top of, CCP allows for the same CCA to be run on different platforms with minimal changes.
+A CCP-based CCA can be directly ran on a completely different host, as long as there exists an existing datapath that implements the CCP standard API.
+\\
+Due to CCP's datapath-reliant nature, the performance of any CCP-based congestion control will heavily depend on the implementation of the underlying datapath, as well as the channel used to communicate between user space and kernel space.
+In our investigations to test the performance of CCP-based CCAs, we decided to build an alternative datapath module that is implemented as an eBPF program rather than a kernel module.
+In addition to providing more safety guarantees, this implementation also allows us to test how the performance of CCP-based CCAs can vary depending on the underlying datapath implementation.
+\\
+
 \end{document}

### 2024-12-07 paper/sections/introduction.tex
feat: Finished intro, related work, and evaluation templates; started on design; refused to use paper: as a commit tag
paper: look over abstract and introduction

--- 2024-12-03 paper/sections/introduction.tex
@@
 \begin{document}
-A paragraph of text goes here. Lots of text. Plenty of interesting
-text. Text text text text text text text text text text text text text
-text text text text text text text text text text text text text text
-text text text text text text text text text text text text text text
-text text text text text text text.
-More fascinating text. Features galore, plethora of promises.
+CCAs form a critical part of the Internet ecosystem.
+While traditional discussions about CCAs centered around ideas like fairness between users (cite flow-based fairness/tcp friendly paper here), newer research explored potentials for CCAs to improve network performance (cite BBR?) and allow the user to customize bandwidth allocated to different applications on the same machine.
+Research on various old and new congestion control algorithms is critical to the stable operation and continuous improvement of the Internet.
+\\
+TCP congestion control forms a critical part of the Internet ecosystem.
+It is often an active area of research, with new algorithms being proposed to improve network performance (cite BBR) and discussions about how CCAs influence fairness between users (cite flow-based fairness/tcp friendly paper here).
+Hence, congestion control research is critical to the stable operation and continuous improvement of the Internet.\\
+A key part of congestion control research involves developing and experimenting with new CCAs. Traditionally, this poses two main problems:
+\begin{enumerate}
+    \item {\bf Development friction}: CCA implements are often split between different datapaths.
+In the Linux kernel, this involves writing kernel code or modules, which presents a high barrier of entry and is prone to bugs that can crash the system.
+    \item {\bf Distribution difficulties}: Pushing a new CCA upstream to the Linux kernel is difficult.
+To see real-world adoption, a new CCA must be user-friendly and easy to adopt in the early stages.
+Being easy to adopt is often predicated on ensuring safety and performance guarantees.
+\end{enumerate}
+To accurately evaluate the impacts of a new CCA on the Internet, it requires significant real-world adoption from users around the world.
+As a result, any CCA wishing to see eventual large-scale adoption must first propose a relatively user-friendly way for people to adopt it in the early stages.
+\\
+With recent advancements in the eBPF space, the possibility of leveraging eBPF as a platform for implementing CCAs has emerged.
+eBPF \cite{ebpf} can be used to write and install programs that run in the Linux kernel with certain safety guarantees.
+Using the \texttt{struct\_ops} API, congestion control-specific hooks can be attached to the TCP stack, allowing for the implementation of new CCAs.
+This approach has the potential to solve both the development friction and distribution difficulties of developing new CCAs.
+The eBPF verifier provides powerful guarantees to the safety of the program, protecting against large amounts of hard-to-solve bugs that lead to the kernel crashing.
+Furthermore, the runtime-attached nature of eBPF makes iterating and testing new versions much easier.
+On the adoption side, the safety guarantees provided by eBPF will greatly encourage user adoption.
+While users can be hesitant in installing kernel patches or modules, attaching a eBPF program can be much lower-risk and appealing.
+\\
+Despite these upsides, running CCAs in eBPF can possibly incur extra costs due to running in the eBPF VM.
+By instrumenting the performance overheads of various different ways of implementing CCAs, this paper explores the degree to which eBPF can be used as a platform for developing CCAs.
+In addition to CCAs directly implemented using eBPF, other means of developing CCAs quickly and safely are also tested.The Congestion Control Plane (CCP) (cite CCP), for example, is an idea proposed to implement CCAs in user space.
+Since the original CCP kernel datapath is written as a Linux kernel module, we also implemented an alternative datapath in eBPF to potentially take advantage of the safety guarantees.
 \end{document}

### 2024-12-07 paper/sections/evaluation.tex
paper: work on design

@@
 \begin{document}
+
+\subsection{Setup and Method}
+We believe that an alternative implementation of an existing CCA can be evaluated using two metrics.
+First, whether or not the behavior of the implementation matches (to a reasonable extent) existing implementations of the same CCA.
+Secondly, the performance costs of the implementation when compared to other implementations.
+We included two sets of benchmarks to measure this: a behavioral benchmark aimed to verify the "correctness" of different implementations (TCP Cubic should behave similarly no matter where it is implemented, as indicated by metrics such as bitrate/congestion window size over time), and a performance benchmark aimed to measure the CPU overhead of different implementation approaches.
+A CCA implementation with smaller CPU overhead would logically lead to a higher maximum bandwidth in an ideal, infinite-speed connection where the CPU running the CCA is the bottleneck.
+\\
+Our benchmarks are ran with iperf3 (cite).
+For each trial, we loop through every CCA we are testing and run iperf3 for 15 seconds.
+At the same time, we run a Python script that loops infinitely and adds 1 to an accumulator at every loop.
+Once the 15 seconds are up, the script then outputs the final number into a file, a higher number suggesting that the script was able to access more CPU cycles.
+We ran 20 trials to ensure statistical reliability.
+Our testing script also included various parameters that can be tuned, including trial duration, reporting intervals, and the metric to be used while generating graphs for the behavioral benchmark.
+\\
+After all the trials, we average the behavioral metric across the trials and plot the average for each CCA through time as the behavioral benchmark.
+We then plot the CPU performances for each CCA across trials on a boxplot.
+\\
+
 In order to make sure we are correctly benchmarking the performance impact of CCAs rather than miscellneous confounding factors, we ran the benchmark on an out-of-the-box Debian image on a VM.
@@
 We also decided to run our benchmarks on various implementations of TCP Cubic due to its wide availability across platforms.
-\\
+
+\subsection{Results}
 The results of behavioral benchmarks are shown in Figure \ref{fig:behavioral}.

### 2024-12-08 paper/sections/evaluation.tex
feat: added citations

@@
 \\
-Our benchmarks are ran with iperf3 (cite).
+Our benchmarks are ran with iperf3 \cite{iperf}.
 For each trial, we loop through every CCA we are testing and run iperf3 for 15 seconds.
@@
 The eBPF implementation of TCP Cubic achieved impressive CPU performance compared to the built-in Linux kernel networking stack implementation.
-CCP-Cubic from the CCP Project (cite generic-cong-avoid git repo) combined with the kernel module + netlink CCP datapath achieved slightly lower performance, where its median is at x percent of the full kernel implementation value.
+CCP-Cubic from the CCP Project \cite{generic-cong-avoid} combined with the kernel module + netlink CCP datapath achieved slightly lower performance, where its median is at x percent of the full kernel implementation value.
 Our implementation of eBPFCCP ranked lower on the performance chart, but was still able to achieve y percent of the full kernel implementation value.

### 2024-12-08 paper/sections/introduction.tex
feat: added citations

@@
 \begin{document}
-CCAs form a critical part of the Internet ecosystem.
-While traditional discussions about CCAs centered around ideas like fairness between users (cite flow-based fairness/tcp friendly paper here), newer research explored potentials for CCAs to improve network performance (cite BBR?) and allow the user to customize bandwidth allocated to different applications on the same machine.
-Research on various old and new congestion control algorithms is critical to the stable operation and continuous improvement of the Internet.
-\\
 TCP congestion control forms a critical part of the Internet ecosystem.
-It is often an active area of research, with new algorithms being proposed to improve network performance (cite BBR) and discussions about how CCAs influence fairness between users (cite flow-based fairness/tcp friendly paper here).
-Hence, congestion control research is critical to the stable operation and continuous improvement of the Internet.\\
+It is often an active area of research, with new algorithms being proposed to improve network performance \cite{CCA-BBR, CCA-FCC} and discussions about how CCAs influence fairness between users \cite{CCAStarvation, CCA-Fairness}.
+Hence, congestion control research is critical to the stable operation and continuous improvement of the Internet, even in a post-flow rate fairness era ~\cite{PrinciplesForCongestionManagement, Dismantling}.\\
 A key part of congestion control research involves developing and experimenting with new CCAs. Traditionally, this poses two main problems:
@@
 By instrumenting the performance overheads of various different ways of implementing CCAs, this paper explores the degree to which eBPF can be used as a platform for developing CCAs.
-In addition to CCAs directly implemented using eBPF, other means of developing CCAs quickly and safely are also tested.The Congestion Control Plane (CCP) (cite CCP), for example, is an idea proposed to implement CCAs in user space.
+In addition to CCAs directly implemented using eBPF, other means of developing CCAs quickly and safely are also tested.The Congestion Control Plane (CCP) \cite{cpp}, for example, is an idea proposed to implement CCAs in user space.
 Since the original CCP kernel datapath is written as a Linux kernel module, we also implemented an alternative datapath in eBPF to potentially take advantage of the safety guarantees.

### 2024-12-10 paper/sections/abstract.tex

--- 2024-12-03 paper/sections/abstract.tex
@@
 \begin{document}
-Your abstract text goes here. Just a few facts. Whet our appetites.
-Not more than 200 words, if possible, and preferably closer to 150.
+This paper seeks to explore the viability of developing Congestion Control Algorithms (CCAs) via eBPF.
+Developing new CCAs has traditionally been a time-consuming and error-prone process.
+Creating these algorithms directly within the Linux kernel demands a high level of kernel programming expertise while still leaving room for bugs that can crash the system.
+Although implementing CCAs as kernel modules has traditionally been an accepted alternative (https://pbg.cs.illinois.edu/papers/jay18pcc-kernel.pdf), it still runs the risk of introducing instability and crashes.
+Recent research has implemented a Congestion Control Plane (CCP) \cite{ccp} that allows CCA developers to implement CCAs in userspace, eliminating the need to run experimental software directly in the kernel.
+This approach involves a carefully designed and safety-checked datapath API; however, the Linux kernel datapath API still relies on a kernel module.
+Simultaneously, developing CCAs in eBPF \cite{ebpf_cca} has emerged as another promising approach, leveraging the eBPF verifier to ensure safety before the code ever runs in the kernel.
+In this paper, we compare these various approaches -- kernel-based, eBPF-based, and userspace (via CCP) -- along with a new hybrid userspace eBPF-based approach (ebpfccp) in terms of behavioral correctness and performance overhead.
 \end{document}

### 2024-12-10 paper/sections/conclusion.tex

--- 2024-12-06 paper/sections/relatedwork.tex
@@
 \begin{document}
-CCP decoupled data gathering and CCA computation.
-A datapath module gathers information regarding a TCP flow and sends it to user space via various methods (such as netlink sockets and unix pipes), while a user space program listens to the given data and sends back any updates to be made to the TCP connection state.
-Platform/OS independence
+Conclusion
 \end{document}

### 2024-12-10 paper/sections/design.tex

--- 2024-12-03 paper/sections/abstract.tex
@@
 \begin{document}
-Your abstract text goes here. Just a few facts. Whet our appetites.
-Not more than 200 words, if possible, and preferably closer to 150.
+
+\begin{figure}[t]
+\centering
+    \includegraphics[width=\columnwidth]{img/ccp-traditional}
+    \caption{CCP's conventional Linux kernel datapath, implemented as a kernel module, utilizes \texttt{libccp} to communicate with the CCP agent.
+        Communication (1) is accomplished via Netlink sockets or a custom character device.
+    }\label{fig:ccptraditional}
+\end{figure}
+
+Figure~\ref{fig:ccptraditional} illustrates the current CCP stack.
+Notably, the CCP algorithm and agent both run in user space, while the datapath is implemented and run completely in kernel space.
+Conventionally, CCP datapath program implementations such as Linux kernel's TCP stack, mTCP, and Google's QUIC all utilize \texttt{libccp} to interface with the CCP agent (Portus) \cite{ccp}.
+
+\subsection{eBPF Implementation}
+
+Due to the eBPF's intense verifier requirements and stipulations, running \texttt{libccp} within the eBPF program was deemed difficult.
+Consequently, we create a user space layer between the CCP agent and the Linux kernel's TCP stack, called eBPFCCP.
+
+eBPFCCP is written in Rust and runs \texttt{libccp} in user space to communicate with the CCP agent while also managing and communicating with the eBPF-based datapath program.
+eBPFCCP's role is to collect primitive congestion signals from the eBPF program, send them over to the CCP agent, and execute instructions sent by the CCP agent to influence TCP behavior.
+As shown in Figure~\ref{fig:ebpfccp}, eBPFCCP communicates with the CCP agent via Unix-domain sockets and interfaces with the eBPF datapath program using BPF hash maps and BPF ring buffers.
+
+\begin{figure}[t]
+\centering
+    \includegraphics[width=\columnwidth]{img/ebpfccp}
+    \caption{The eBPFCCP stack runs \texttt{libccp} in user space, communicating (1) with the CCP agent via Unix-domain sockets and interfacing with the eBPF datapath program via (2) BPF hash maps and (3) BPF ring buffers.
+    }\label{fig:ebpfccp}
+\end{figure}
+
+On the eBPF datapath side, we use eBPF's \texttt{struct\_ops} API to attach congestion control-specific hooks to the TCP stack.
+Each of these hooks operate on a per-flow basis.
+When a new flow is created, the eBPF datapath program records the flow's information in a BPF ring buffer called \texttt{create\_conn\_events}.
+This signals eBPFCCP to retrieve the new flow's information and pass it to the CCP agent.
+Similarly, when a flow is terminated, the eBPF datapath program writes an event to the \texttt{free\_conn\_events} ring buffer, which eBPFCCP reads to perform flow cleanup actions.
+As new ACKs arrive, the eBPF datapath program reads the TCP state and calculates primitive congestion signals, which are then written to the \texttt{signals} ring buffer, read by eBPFCCP, and sent to the CCP agent.
+Then, the message the CCP agent sends back to the eBPFCCP pertaining to window size and pacing rate is written to the \texttt{connections} hash map, which the eBPF datapath program reads and updates the TCP state accordingly.
+The BPF maps used by the eBPF datapath and eBPFCCP are summarized in Table~\ref{tab:maptable}.
+
+\begin{table}[htbp]
+    \centering
+    \footnotesize
+    \begin{tabular}{@{}p{0.35\columnwidth} p{0.5\columnwidth}@{}}
+        \toprule
+        \textbf{Map} & \textbf{Description} \\[3pt]
+        \midrule
+        \texttt{connections} (BPF Hash) &
+        eBPFCCP writes per-flow congestion window size and pacing rate. 
+        The eBPF datapath reads these values and updates the TCP state accordingly. \\[6pt]
+
+        \texttt{signals} (BPF Ringbuf) &
+        The eBPF datapath writes primitive signal measurements into this buffer. 
+        The eBPFCCP reads these measurements and forwards them to the CCP agent. \\[6pt]
+
+        \texttt{create\_conn\_events} (BPF Ringbuf) &
+        Whenever a new flow is created, the eBPF datapath records flow information here. 
+        The eBPFCCP then retrieves and passes these details to the CCP agent. \\[6pt]
+
+        \texttt{free\_conn\_events} (BPF Ringbuf) &
+        Upon flow termination, the eBPF datapath writes an event. 
+        The eBPFCCP reads and relays this information to the CCP agent for flow cleanup actions. \\[3pt]
+        \bottomrule
+    \end{tabular}
+    \caption{BPF Maps used by the eBPF datapath and eBPFCCP for managing flow states, signals, and events.}
+    \label{tab:maptable}
+\end{table}
+
+Overall, the eBPFCCP aims to act as a bridge between the CCP agent and the eBPF datapath program.
+
 \end{document}

### 2024-12-11 paper/sections/evaluation.tex
feat: finished evaluation and conclusion sections

@@
 \subsection{Results}
-The results of behavioral benchmarks are shown in Figure \ref{fig:behavioral}.
-From the graph, we can see that [to-be-added-conclusion].
-The results of CPU benchmarks are shown in Figure \ref{fig:cpu}.
+
+\begin{figure}[t]
+    \centering
+        \includegraphics[width=\columnwidth]{img/cca-behavior-cwnd}
+        \caption{snd-cwnd behavior of TCP Cubic across different platforms of implementation. Averaged over 20 trials.
+        }\label{fig:cca-behavior-cwnd}
+    \end{figure}
+
+\begin{figure}[t]
+    \centering
+        \includegraphics[width=\columnwidth]{img/cca-behavior-bitrate}
+        \caption{Bitrate behavior of TCP Cubic across different platforms of implementation. Averaged over 20 trials.
+        }\label{fig:cca-behavior-bitrate}
+    \end{figure}
+
+\begin{figure}[t]
+    \centering
+        \includegraphics[width=\columnwidth]{img/cca-behavior-rtt}
+        \caption{RTT behavior of TCP Cubic across different platforms of implementation. Averaged over 20 trials.
+        }\label{fig:cca-behavior-rtt}
+    \end{figure}
+
+\begin{figure}[t]
+    \centering
+        \includegraphics[width=\columnwidth]{img/cca-performance}
+        \caption{Standard box plot of TCP Cubic CPU performance across different platforms of implementation.
+Higher is better.
+Box extends from 25th to 75th percentile.
+Whiskers extend to the farthest data point within 1.5 IQR from the box.
+Data gathered over 20 trials.
+        }\label{fig:cca-performance}
+    \end{figure}
+
+The results of behavioral benchmarks are shown in Figures~\ref{fig:cca-behavior-cwnd},~\ref{fig:cca-behavior-bitrate}, and~\ref{fig:cca-behavior-rtt}.
+From the graph, we can see that the behavior of the same Congestion Control Algorithm remains similar across multiple platforms of integration.
+These results gives us confidence on the correctness of all the implementation platforms involved, and allows us to proceed to performance benchmarking.
+The results of CPU benchmarks are shown in Figure \ref{fig:cca-performance}.
 The eBPF implementation of TCP Cubic achieved impressive CPU performance compared to the built-in Linux kernel networking stack implementation.
@@
 Our implementation of eBPFCCP ranked lower on the performance chart, but was still able to achieve y percent of the full kernel implementation value.
-Due to the relative comparability of CPU performance between the kernel and eBPF implementations of TCP Cubicm, we theorize the noticable gap between eBPFCCP and kernel module CCP was due to our choice of using unix pipes rather than netlink as a channel for communicating between the eBPFCCP and the user space program.
+Due to the relative comparability of CPU performance between the kernel and eBPF implementations of TCP Cubicm, we theorize the gap between eBPFCCP and kernel module CCP was due to our choice of using unix pipes rather than netlink as a channel for communicating between the eBPFCCP and the user space program.
 \\
@@
 The negligible performance overhead when compared to the kernel native implementation is impressive, and suggests that eBPF-CCAs can possibly also be used as a long-term deployment option outside of research and development stages.
+With regards to CCP, while the performance overhead of eBPFCCP is non-negligible, it should be noted that the benchmark is performed on a single core VM.
+In a real-world scenario, the performance overhead of eBPFCCP is likely to be negligible for all but the most performance-sensitive industry networking applications.
+The safety guarantees provided by eBPFCCP would provide a good intermediate step for users to adopt and experiment with a new CCA before it is natively implemented either directly into the kernel or as an eBPF program.
 \end{document}

### 2024-12-11 paper/main.tex
paper: work on design
chore: small template removal

@@
 \usepackage{subfiles}
+\usepackage{booktabs}
 
@@
 
-\subsection{LaTeX-ing Your TeX File}
+\subsection{Acknowledgements and Availability}
 %-----------------------------------
 
-People often use \texttt{pdflatex} these days for creating pdf-s from
-tex files via the shell. And \texttt{bibtex}, of course. Works for us.
-
-%-------------------------------------------------------------------------------
-\section*{Acknowledgments}
-%-------------------------------------------------------------------------------
-
-The USENIX latex style is old and very tired, which is why
-there's no \textbackslash{}acks command for you to use when
-acknowledging. Sorry.
-
-%-------------------------------------------------------------------------------
-\section*{Availability}
-%-------------------------------------------------------------------------------
-
-USENIX program committees give extra points to submissions that are
-backed by artifacts that are publicly available. If you made your code
-or data available, it's worth mentioning this fact in a dedicated
-section.
+We would like to thank Brown's CS2680 and Professor Akshay Narayan for the help provided in the development of this project.
+The source code for this project is available at \url{https://github.com/claby2/ebpfcca}
 

### 2024-12-11 paper/main.tex
chore: artifact clarification

@@
 
-%% ANYTHING BELOW HERE IS FROM THE ORIGINAL TEMPLATE, SHOULD BE REMOVED LATER
-
-%-------------------------------------------------------------------------------
-\section{Footnotes, Verbatim, and Citations}
-%-------------------------------------------------------------------------------
-
-Footnotes should be places after punctuation characters, without any
-spaces between said characters and footnotes, like so.%
-\footnote{Remember that USENIX format stopped using endnotes and is
-  now using regular footnotes.} And some embedded literal code may
-look as follows.
-
-\begin{verbatim}
-int main(int argc, char *argv[]) 
-{
-    return 0;
-}
-\end{verbatim}
-
-Now we're going to cite somebody. Watch for the cite tag. Here it
-comes. Arpachi-Dusseau and Arpachi-Dusseau co-authored an excellent OS
-book, which is also really funny~\cite{arpachiDusseau18:osbook}, and
-Waldspurger got into the SIGOPS hall-of-fame due to his seminal paper
-about resource management in the ESX hypervisor~\cite{waldspurger02}.
-
-The tilde character (\~{}) in the tex source means a non-breaking
-space. This way, your reference will always be attached to the word
-that preceded it, instead of going to the next line.
-
-And the 'cite' package sorts your citations by their numerical order
-of the corresponding references at the end of the paper, ridding you
-from the need to notice that, e.g, ``Waldspurger'' appears after
-``Arpachi-Dusseau'' when sorting references
-alphabetically~\cite{waldspurger02,arpachiDusseau18:osbook}.
-
-It'd be nice and thoughtful of you to include a suitable link in each
-and every bibtex entry that you use in your submission, to allow
-reviewers (and other readers) to easily get to the cited work, as is
-done in all entries found in the References section of this document.
-
-Now we're going take a look at Section~\ref{sec:figs}, but not before
-observing that refs to sections and citations and such are colored and
-clickable in the PDF because of the packages we've included.
-
-%-------------------------------------------------------------------------------
-\section{Floating Figures and Lists}
-\label{sec:figs}
-%-------------------------------------------------------------------------------
-
-%---------------------------
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}
-  \draw[thin,gray!40] (-2,-2) grid (2,2);
-  \draw[<->] (-2,0)--(2,0) node[right]{$x$};
-  \draw[<->] (0,-2)--(0,2) node[above]{$y$};
-  \draw[line width=2pt,blue,-stealth](0,0)--(1,1)
-        node[anchor=south west]{$\boldsymbol{u}$};
-  \draw[line width=2pt,red,-stealth](0,0)--(-1,-1)
-        node[anchor=north east]{$\boldsymbol{-u}$};
-\end{tikzpicture}
-\end{center}
-\caption{\label{fig:vectors} Text size inside figure should be as big as
-  caption's text. Text size inside figure should be as big as
-  caption's text. Text size inside figure should be as big as
-  caption's text. Text size inside figure should be as big as
-  caption's text. Text size inside figure should be as big as
-  caption's text. }
-\end{figure}
-%% %---------------------------
-
-Here's a typical reference to a floating figure:
-Figure~\ref{fig:vectors}. Floats should usually be placed where latex
-wants then. Figure\ref{fig:vectors} is centered, and has a caption
-that instructs you to make sure that the size of the text within the
-figures that you use is as big as (or bigger than) the size of the
-text in the caption of the figures. Please do. Really.
-
-In our case, we've explicitly drawn the figure inlined in latex, to
-allow this tex file to cleanly compile. But usually, your figures will
-reside in some file.pdf, and you'd include them in your document
-with, say, \textbackslash{}includegraphics.
-
-Lists are sometimes quite handy. If you want to itemize things, feel
-free:
-
-\begin{description}
-
-\item[fread] a function that reads from a \texttt{stream} into the
-  array \texttt{ptr} at most \texttt{nobj} objects of size
-  \texttt{size}, returning returns the number of objects read.
-
-\item[Fred] a person's name, e.g., there once was a dude named Fred
-  who separated usenix.sty from this file to allow for easy
-  inclusion.
-\end{description}
-
-\noindent
-The noindent at the start of this paragraph in its tex version makes
-it clear that it's a continuation of the preceding paragraph, as
-opposed to a new paragraph in its own right.
-
-\subsection{Acknowledgements and Availability}
+\section{Acknowledgements and Availability}
 %-----------------------------------
@@
 We would like to thank Brown's CS2680 and Professor Akshay Narayan for the help provided in the development of this project.
-The source code for this project is available at \url{https://github.com/claby2/ebpfcca}
+The source code for all the artifacts (eBPF-Cubic, eBPFCCP, benchmark suite) is available at \url{https://github.com/claby2/ebpfcca}
 

### 2024-12-12 paper/main.tex
feat: Finished paper

--- 2024-12-07 paper/main.tex
@@
 %-------------------------------------------------------------------------------
-@Book{arpachiDusseau18:osbook,
-  author =       {Arpaci-Dusseau, Remzi H. and Arpaci-Dusseau Andrea C.},
-  title =        {Operating Systems: Three Easy Pieces},
-  publisher =    {Arpaci-Dusseau Books, LLC},
-  year =         2015,
-  edition =      {1.00},
-  note =         {\url{http://pages.cs.wisc.edu/~remzi/OSTEP/}}
+@misc{ebpf,
+  key = {eBPF}
+  title =        {Linux Socket Filtering aka Berkeley Packet Filter (BPF)},
+  howpublished =         {\url{https://www.kernel.org/doc/Documentation/networking/filter.txt}}
+  note = {Accessed: 2024-12-08}
 }
-@InProceedings{waldspurger02,
-  author =       {Waldspurger, Carl A.},
-  title =        {Memory resource management in {VMware ESX} server},
-  booktitle =    {USENIX Symposium on Operating System Design and
-                  Implementation (OSDI)},
-  year =         2002,
-  pages =        {181--194},
-  note =         {\url{https://www.usenix.org/legacy/event/osdi02/tech/waldspurger/waldspurger.pdf}}}
+@inproceedings{ccp,
+    title={Restructuring endpoint congestion control},
+    ISBN={9781450355674},
+    url={https://dl.acm.org/doi/10.1145/3230543.3230553},
+    DOI={10.1145/3230543.3230553},
+    booktitle={SIGCOMM},
+    author={Narayan, Akshay and Cangialosi, Frank and Raghavan, Deepti and Goyal, Prateesh and Narayana, Srinivas and Mittal, Radhika and Alizadeh, Mohammad and Balakrishnan, Hari},
+    year={2018},
+}
+@inproceedings{ebpf_cca,
+author = {Hinz, J\"{o}rn-Thorben and Addanki, Vamsi and Gy\"{o}rgyi, Csaba and Jepsen, Theo and Schmid, Stefan},
+title = {TCP's Third Eye: Leveraging eBPF for Telemetry-Powered Congestion Control},
+year = {2023},
+isbn = {9798400702938},
+publisher = {Association for Computing Machinery},
+url = {https://doi.org/10.1145/3609021.3609295},
+doi = {10.1145/3609021.3609295},
+booktitle = {Proceedings of the 1st Workshop on EBPF and Kernel Extensions},
+series = {eBPF '23}
+}
+@inproceedings{CCAStarvation,
+author = {Arun, Venkat and Alizadeh, Mohammad and Balakrishnan, Hari},
+title = {Starvation in end-to-end congestion control},
+year = {2022},
+isbn = {9781450394208},
+publisher = {Association for Computing Machinery},
+address = {New York, NY, USA},
+url = {https://doi.org/10.1145/3544216.3544223},
+doi = {10.1145/3544216.3544223},
+abstract = {To overcome weaknesses in traditional loss-based congestion control algorithms (CCAs), researchers have developed and deployed several delay-bounding CCAs that achieve high utilization without bloating delays (e.g., Vegas, FAST, BBR, PCC, Copa, etc.).
+When run on a path with a fixed bottleneck rate, these CCAs converge to a small delay range in equilibrium.
+This paper proves a surprising result: although designed to achieve reasonable inter-flow fairness, current methods to develop delay-bounding CCAs cannot always avoid starvation, an extreme form of unfairness.
+Starvation may occur when such a CCA runs on paths where non-congestive network delay variations due to real-world factors such as ACK aggregation and end-host scheduling exceed double the delay range that the CCA converges to in equilibrium.
+We provide experimental evidence for this result for BBR, PCC Vivace, and Copa with a link emulator.
+We discuss the implications of this result and posit that to guarantee no starvation an efficient delay-bounding CCA should design for a certain amount of non-congestive jitter and ensure that its equilibrium delay oscillations are at least one-half of this jitter.},
+booktitle = {Proceedings of the ACM SIGCOMM 2022 Conference},
+pages = {177–192},
+numpages = {16},
+keywords = {starvation, delay-convergence, congestion control},
+location = {Amsterdam, Netherlands},
+series = {SIGCOMM '22}
+}
+@INPROCEEDINGS{CCA-Fairness,
+  author={Ling, Yang and Xiao-fan, Zhang and Yu-shan, Liu},
+  booktitle={2009 International Conference on Wireless Communications & Signal Processing}, 
+  title={Analyzing and improving the TCP flow fairness in 802.11 based ad hoc networks}, 
+  year={2009},
+  volume={},
+  number={},
+  pages={1-5},
+  keywords={Ad hoc networks;Spread spectrum communication;Information science;Information analysis;Costs;Monopoly;Aggregates;Throughput;Media Access Protocol;Quantization;Ad Hoc networks;IEEE 802.11 DCF;TCP flow fairness;Probability model},
+  doi={10.1109/WCSP.2009.5371583}}
+
+@inproceedings{CCA-FCC,
+author = {Che, Biyao and Wang, Yuxiang and Wan, Zirui and Chen, Ying and Wang, Zixiao and Tian, Yuan and Zhao, Jizhuang and Wang, Shuo and Zhang, Jiao},
+title = {FCC : A Fast-Converging Low-Latency Congestion Control Algorithm for Datacenter RDMA Network},
+year = {2024},
+isbn = {9798400717581},
+publisher = {Association for Computing Machinery},
+address = {New York, NY, USA},
+url = {https://doi.org/10.1145/3663408.3665834},
+doi = {10.1145/3663408.3665834},
+abstract = {Congestion control plays a crucial role in ensuring the performance of data center networks.
+However, mainstream RDMA congestion control algorithms still face challenges such as slow congestion response and poor deployability.
+In this paper, we propose a novel fast-convergence congestion control algorithm, FCC, to address these shortcomings.
+FCC leverages Explicit Congestion Notification (ECN) and Round-Trip Time (RTT) signals, utilizing the gradient of RTT to enhance response speed and employing a Sigmoid curve for rate increment.
+Through experiments, we demonstrate that compared to existing state-of-the-art algorithms, FCC achieves superior performance in terms of convergence speed, fairness, and small flow latency metrics.},
+booktitle = {Proceedings of the 8th Asia-Pacific Workshop on Networking},
+pages = {200–201},
+numpages = {2},
+keywords = {ECN, RDMA congestion control, RTT, Sigmoid-AI.},
+location = {Sydney, Australia},
+series = {APNet '24}
+}
+@article{CCA-BBR,
+author = {Cardwell, Neal and Cheng, Yuchung and Gunn, C. Stephen and Yeganeh, Soheil Hassas and Jacobson, Van},
+title = {BBR: Congestion-Based Congestion Control: Measuring bottleneck bandwidth and round-trip propagation time},
+year = {2016},
+issue_date = {September-October 2016},
+publisher = {Association for Computing Machinery},
+address = {New York, NY, USA},
+volume = {14},
+number = {5},
+issn = {1542-7730},
+url = {https://doi.org/10.1145/3012426.3022184},
+doi = {10.1145/3012426.3022184},
+abstract = {When bottleneck buffers are large, loss-based congestion control keeps them full, causing bufferbloat.
+When bottleneck buffers are small, loss-based congestion control misinterprets loss as a signal of congestion, leading to low throughput.
+Fixing these problems requires an alternative to loss-based congestion control.
+Finding this alternative requires an understanding of where and how network congestion originates.},
+journal = {Queue},
+month = oct,
+pages = {20–53},
+numpages = {34}
+}
+@inproceedings{PrinciplesForCongestionManagement,
+author = {Brown, Lloyd and Alcoz, Albert Gran and Cangialosi, Frank and Narayan, Akshay and Alizadeh, Mohammad and Balakrishnan, Hari and Friedman, Eric and Katz-Bassett, Ethan and Krishnamurthy, Arvind and Schapira, Michael and Shenker, Scott},
+title = {Principles for Internet Congestion Management},
+year = {2024},
+isbn = {9798400706141},
+publisher = {Association for Computing Machinery},
+address = {New York, NY, USA},
+url = {https://doi.org/10.1145/3651890.3672247},
+doi = {10.1145/3651890.3672247},
+abstract = {Given the technical flaws with---and the increasing non-observance of---the TCP-friendliness paradigm, we must rethink how the Internet should manage bandwidth allocation.
+We explore this question from first principles, but remain within the constraints of the Internet's current architecture and commercial arrangements.
+We propose a new framework, Recursive Congestion Shares (RCS), that provides bandwidth allocations independent of which congestion control algorithms flows use but consistent with the Internet's economics.
+We show that RCS achieves this goal using game-theoretic calculations and simulations as well as network emulation.},
+booktitle = {Proceedings of the ACM SIGCOMM 2024 Conference},
+pages = {166–180},
+numpages = {15},
+keywords = {network architecture},
+location = {Sydney, NSW, Australia},
+series = {ACM SIGCOMM '24}
+}
+@article{Dismantling,
+author = {Briscoe, Bob},
+title = {Flow rate fairness: dismantling a religion},
+year = {2007},
+issue_date = {April 2007},
+publisher = {Association for Computing Machinery},
+address = {New York, NY, USA},
+volume = {37},
+number = {2},
+issn = {0146-4833},
+url = {https://doi.org/10.1145/1232919.1232926},
+doi = {10.1145/1232919.1232926},
+abstract = {Resource allocation and accountability keep reappearing on every list of requirements for the Internet architecture.
+The reason we never resolve these issues is a broken idea of what the problem is.
+The applied research and standards communities are using completely unrealistic and impractical fairness criteria.
+The resulting mechanisms don't even allocate the right thing and they don't allocate it between the right entities.
+We explain as bluntly as we can that thinking about fairness mechanisms like TCP in terms of sharing out flow rates has no intellectual heritage from any concept of fairness in philosophy or social science, or indeed real life.
+Comparing flow rates should never again be used for claims of fairness in production networks.
+Instead, we should judge fairness mechanisms on how they share out the 'cost' of each user's actions on others},
+journal = {SIGCOMM Comput. Commun. Rev.},
+month = mar,
+pages = {63–74},
+numpages = {12},
+keywords = {resource allocation, identity, fairness, congestion control, accountability}
+}
+@misc{iperf,
+  author = {The iPerf team},
+  title =        {iPerf - The ultimate speed test tool for TCP, UDP and SCTP},
+  howpublished =         {\url{https://iperf.fr/}}
+  notenote = {Accessed: 2024-11-12}
+}
+@misc{generic-cong-avoid,
+  author = {The CCP Project},
+  title =        {CCP Algorithm: Generic Congestion Avoidance},
+  howpublished =         {\url{https://github.com/ccp-project/generic-cong-avoid}}
+  note = {Accessed: 2024-11-12}
+}
 \end{filecontents}

### 2024-12-12 paper/main.tex

@@
 
-%% ANYTHING BELOW HERE IS FROM THE ORIGINAL TEMPLATE, SHOULD BE REMOVED LATER
-
-%-------------------------------------------------------------------------------
-\section{Footnotes, Verbatim, and Citations}
-%-------------------------------------------------------------------------------
-
-Footnotes should be places after punctuation characters, without any
-spaces between said characters and footnotes, like so.%
-\footnote{Remember that USENIX format stopped using endnotes and is
-  now using regular footnotes.} And some embedded literal code may
-look as follows.
-
-\begin{verbatim}
-int main(int argc, char *argv[]) 
-{
-    return 0;
-}
-\end{verbatim}
-
-Now we're going to cite somebody. Watch for the cite tag. Here it
-comes. Arpachi-Dusseau and Arpachi-Dusseau co-authored an excellent OS
-book, which is also really funny~\cite{arpachiDusseau18:osbook}, and
-Waldspurger got into the SIGOPS hall-of-fame due to his seminal paper
-about resource management in the ESX hypervisor~\cite{waldspurger02}.
-
-The tilde character (\~{}) in the tex source means a non-breaking
-space. This way, your reference will always be attached to the word
-that preceded it, instead of going to the next line.
-
-And the 'cite' package sorts your citations by their numerical order
-of the corresponding references at the end of the paper, ridding you
-from the need to notice that, e.g, ``Waldspurger'' appears after
-``Arpachi-Dusseau'' when sorting references
-alphabetically~\cite{waldspurger02,arpachiDusseau18:osbook}.
-
-It'd be nice and thoughtful of you to include a suitable link in each
-and every bibtex entry that you use in your submission, to allow
-reviewers (and other readers) to easily get to the cited work, as is
-done in all entries found in the References section of this document.
-
-Now we're going take a look at Section~\ref{sec:figs}, but not before
-observing that refs to sections and citations and such are colored and
-clickable in the PDF because of the packages we've included.
-
-%-------------------------------------------------------------------------------
-\section{Floating Figures and Lists}
-\label{sec:figs}
-%-------------------------------------------------------------------------------
-
-%---------------------------
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}
-  \draw[thin,gray!40] (-2,-2) grid (2,2);
-  \draw[<->] (-2,0)--(2,0) node[right]{$x$};
-  \draw[<->] (0,-2)--(0,2) node[above]{$y$};
-  \draw[line width=2pt,blue,-stealth](0,0)--(1,1)
-        node[anchor=south west]{$\boldsymbol{u}$};
-  \draw[line width=2pt,red,-stealth](0,0)--(-1,-1)
-        node[anchor=north east]{$\boldsymbol{-u}$};
-\end{tikzpicture}
-\end{center}
-\caption{\label{fig:vectors} Text size inside figure should be as big as
-  caption's text. Text size inside figure should be as big as
-  caption's text. Text size inside figure should be as big as
-  caption's text. Text size inside figure should be as big as
-  caption's text. Text size inside figure should be as big as
-  caption's text. }
-\end{figure}
-%% %---------------------------
-
-Here's a typical reference to a floating figure:
-Figure~\ref{fig:vectors}. Floats should usually be placed where latex
-wants then. Figure\ref{fig:vectors} is centered, and has a caption
-that instructs you to make sure that the size of the text within the
-figures that you use is as big as (or bigger than) the size of the
-text in the caption of the figures. Please do. Really.
-
-In our case, we've explicitly drawn the figure inlined in latex, to
-allow this tex file to cleanly compile. But usually, your figures will
-reside in some file.pdf, and you'd include them in your document
-with, say, \textbackslash{}includegraphics.
-
-Lists are sometimes quite handy. If you want to itemize things, feel
-free:
-
-\begin{description}
-
-\item[fread] a function that reads from a \texttt{stream} into the
-  array \texttt{ptr} at most \texttt{nobj} objects of size
-  \texttt{size}, returning returns the number of objects read.
-
-\item[Fred] a person's name, e.g., there once was a dude named Fred
-  who separated usenix.sty from this file to allow for easy
-  inclusion.
-\end{description}
-
-\noindent
-The noindent at the start of this paragraph in its tex version makes
-it clear that it's a continuation of the preceding paragraph, as
-opposed to a new paragraph in its own right.
-
-\subsection{LaTeX-ing Your TeX File}
+\section{Acknowledgements and Availability}
 %-----------------------------------
 
-People often use \texttt{pdflatex} these days for creating pdf-s from
-tex files via the shell. And \texttt{bibtex}, of course. Works for us.
-
-%-------------------------------------------------------------------------------
-\section*{Acknowledgments}
-%-------------------------------------------------------------------------------
-
-The USENIX latex style is old and very tired, which is why
-there's no \textbackslash{}acks command for you to use when
-acknowledging. Sorry.
-
-%-------------------------------------------------------------------------------
-\section*{Availability}
-%-------------------------------------------------------------------------------
-
-USENIX program committees give extra points to submissions that are
-backed by artifacts that are publicly available. If you made your code
-or data available, it's worth mentioning this fact in a dedicated
-section.
+We would like to thank Brown's CS2680 and Professor Akshay Narayan for the help provided in the development of this project.
+The source code for all the artifacts (eBPF-Cubic, eBPFCCP, benchmark suite) is available at \url{https://github.com/claby2/ebpfcca}
 

### 2024-12-12 paper/sections/conclusion.tex

@@
 \begin{document}
-Conclusion
+In this paper, we have evaluated the various attributes of eBPF as a platform for CCA implementation.
+First, through our behavior evaluations, we have shown that CCAs implemented through alterantive platforms (eBPF, CCP, eBPFCCP) do achieve behavioral correctness.
+We have also shown that eBPF is a viable platform for developing CCAs natively on, with negligible performance overhead compared to the kernel native implementation.
+Our implementation of eBPFCCP had a higher performance overhead, but was still able to achieve a significant percentage of the full kernel implementation value.
+We believe this artifact can be useful as an alternative CCP datapath that provides safety guarantees.
+Overall, the data demonstrates that using eBPF-related CCA platforms not only provides many benefits to development speed and safety, but can also be used as a long-term deployment option outside of research stages.
 \end{document}

### 2024-12-12 paper/main.tex
Update main.tex

@@
 @misc{ebpf,
-  key = {eBPF}
+  key = {eBPF},
   title =        {Linux Socket Filtering aka Berkeley Packet Filter (BPF)},
-  howpublished =         {\url{https://www.kernel.org/doc/Documentation/networking/filter.txt}}
+  howpublished =         {\url{https://www.kernel.org/doc/Documentation/networking/filter.txt}},
   note = {Accessed: 2024-12-08}
@@
   title =        {iPerf - The ultimate speed test tool for TCP, UDP and SCTP},
-  howpublished =         {\url{https://iperf.fr/}}
+  howpublished =         {\url{https://iperf.fr/}},
   notenote = {Accessed: 2024-11-12}
@@
   title =        {CCP Algorithm: Generic Congestion Avoidance},
-  howpublished =         {\url{https://github.com/ccp-project/generic-cong-avoid}}
+  howpublished =         {\url{https://github.com/ccp-project/generic-cong-avoid}},
   note = {Accessed: 2024-11-12}

### 2024-12-12 paper/sections/abstract.tex
paper: revise

@@
 Creating these algorithms directly within the Linux kernel demands a high level of kernel programming expertise while still leaving room for bugs that can crash the system.
-Although implementing CCAs as kernel modules has traditionally been an accepted alternative (https://pbg.cs.illinois.edu/papers/jay18pcc-kernel.pdf), it still runs the risk of introducing instability and crashes.
-Recent research has implemented a Congestion Control Plane (CCP) \cite{ccp} that allows CCA developers to implement CCAs in userspace, eliminating the need to run experimental software directly in the kernel.
+Although implementing CCAs as kernel modules has traditionally been an accepted alternative \cite{Jay2018APK}, it still runs the risk of introducing instability and crashes.
+Recent research has implemented a Congestion Control Plane (CCP) \cite{ccp} that allows CCA developers to implement CCAs in user space, eliminating the need to run experimental software directly in the kernel.
 This approach involves a carefully designed and safety-checked datapath API; however, the Linux kernel datapath API still relies on a kernel module.
 Simultaneously, developing CCAs in eBPF \cite{ebpf_cca} has emerged as another promising approach, leveraging the eBPF verifier to ensure safety before the code ever runs in the kernel.
-In this paper, we compare these various approaches -- kernel-based, eBPF-based, and userspace (via CCP) -- along with a new hybrid userspace eBPF-based approach (ebpfccp) in terms of behavioral correctness and performance overhead.
+In this paper, we compare these various approaches -- kernel-based, eBPF-based, and user space (via CCP) -- along with a new hybrid user space eBPF-based approach (ebpfccp) in terms of behavioral correctness and performance overhead.
 \end{document}

### 2024-12-12 paper/sections/conclusion.tex
paper: revise

--- 2024-12-10 paper/sections/conclusion.tex
@@
 \begin{document}
-Conclusion
+In this paper, we introduced an eBPF-based platform called eBPFCCP, which enables the implementation of user space CCAs.
+We then compared eBPFCCP with the native Linux kernel TCP stack, a pure eBPF implementation, and CCP.
+Our evaluations focused on the behavioral correctness and performance impact of these implementations.
+Through our behavior evaluations, we demonstrated that CCAs implemented using alternative platforms achieve the desired behavior.
+Additionally, we showed that eBPF is a suitable platform for developing CCAs natively, with negligible performance overhead compared to the kernel’s native implementation.
+While our implementation of eBPFCCP had a slightly higher performance overhead, it still achieved a substantial percentage of the full kernel implementation’s value.
+We believe that eBPFCCP can be valuable as an alternative CCP datapath that offers safety guarantees.
+Overall, the data presented here demonstrates that using eBPF-related CCA platforms not only provides numerous benefits, including enhanced development speed and safety, but also has the potential for long-term deployment beyond research stages.
 \end{document}

### 2024-12-12 paper/sections/evaluation.tex
paper: revise

@@
 \subsection{Setup and Method}
-We believe that an alternative implementation of an existing CCA can be evaluated using two metrics.
-First, whether or not the behavior of the implementation matches (to a reasonable extent) existing implementations of the same CCA.
-Secondly, the performance costs of the implementation when compared to other implementations.
-We included two sets of benchmarks to measure this: a behavioral benchmark aimed to verify the "correctness" of different implementations (TCP Cubic should behave similarly no matter where it is implemented, as indicated by metrics such as bitrate/congestion window size over time), and a performance benchmark aimed to measure the CPU overhead of different implementation approaches.
+An alternative implementation of an existing CCA can be evaluated using two metrics.
+We evaluate eBPFCCP using two metrics:
+\begin{enumerate}
+    \item {\bf Behavior}: how accurate is eBPFCCP in replicating original CCA behavior?
+    \item {\bf Performance}: what is the performance overhead of eBPFCCP?
+\end{enumerate}
+
+We included two sets of benchmarks to measure this: (1) a behavioral benchmark aimed to verify the "correctness" of different implementations (TCP Cubic should behave similarly no matter where it is implemented, as indicated by metrics such as bitrate/congestion window size over time), and (2) a performance benchmark aimed to measure the CPU overhead of different implementation approaches.
 A CCA implementation with smaller CPU overhead would logically lead to a higher maximum bandwidth in an ideal, infinite-speed connection where the CPU running the CCA is the bottleneck.
 \\
-Our benchmarks are ran with iperf3 \cite{iperf}.
-For each trial, we loop through every CCA we are testing and run iperf3 for 15 seconds.
-At the same time, we run a Python script that loops infinitely and adds 1 to an accumulator at every loop.
-Once the 15 seconds are up, the script then outputs the final number into a file, a higher number suggesting that the script was able to access more CPU cycles.
-We ran 20 trials to ensure statistical reliability.
-Our testing script also included various parameters that can be tuned, including trial duration, reporting intervals, and the metric to be used while generating graphs for the behavioral benchmark.
+Our benchmarks utilize iperf3 \cite{iperf}.
+For each trial, we loop through every CCA we are testing and run iperf3 for $15$ seconds.
+At the same time, we run a Python script that loops infinitely while incrementing a variable.
+Once the $15$ seconds are up, the script then outputs the final number into a file.
+A higher output number suggests that the script went through more CPU cycles during the trial, indicating better CPU performance.
+We a ran a total of $20$ trials.
 \\
@@
 \\
-
-In order to make sure we are correctly benchmarking the performance impact of CCAs rather than miscellneous confounding factors, we ran the benchmark on an out-of-the-box Debian image on a VM.
-To ensure the CPU benchmark and the CCA are running on the same CPU, our VM is set up to contain only one core.
+To make sure we are correctly benchmarking the performance impact of CCAs rather than miscellneous confounding factors, we ran the benchmark on an out-of-the-box Debian image on a VM.
+To ensure the CPU benchmark and the CCA are running on the same core, our VM is set up to use only one core.
 We also decided to run our benchmarks on various implementations of TCP Cubic due to its wide availability across platforms.
@@
 
-The results of behavioral benchmarks are shown in Figures~\ref{fig:cca-behavior-cwnd},~\ref{fig:cca-behavior-bitrate}, and~\ref{fig:cca-behavior-rtt}.
-From the graph, we can see that the behavior of the same Congestion Control Algorithm remains similar across multiple platforms of integration.
-These results gives us confidence on the correctness of all the implementation platforms involved, and allows us to proceed to performance benchmarking.
-The results of CPU benchmarks are shown in Figure \ref{fig:cca-performance}.
-The eBPF implementation of TCP Cubic achieved impressive CPU performance compared to the built-in Linux kernel networking stack implementation.
-CCP-Cubic from the CCP Project \cite{generic-cong-avoid} combined with the kernel module + netlink CCP datapath achieved slightly lower performance, where its median is at x percent of the full kernel implementation value.
+The results of the behavioral benchmarks are shown in Figures~\ref{fig:cca-behavior-cwnd},~\ref{fig:cca-behavior-bitrate}, and~\ref{fig:cca-behavior-rtt}.
+From the graphs, we can see that the behavior of the same Congestion Control Algorithm remains similar across congestion window size, bitrate, and RTT.
+The results of the CPU benchmarks are shown in Figure \ref{fig:cca-performance}.
+The eBPF implementation of TCP Cubic achieved similar CPU performance compared to the built-in Linux kernel networking stack implementation.
+CCP-Cubic from the CCP Project \cite{generic-cong-avoid} combined with the CCP datapath kernel module and netlink slightly lower performance, where its median is at x percent of the full kernel implementation value.
 Our implementation of eBPFCCP ranked lower on the performance chart, but was still able to achieve y percent of the full kernel implementation value.
@@
 From these results, we can conclude that eBPF is a viable platform for the development CCAs.
-The negligible performance overhead when compared to the kernel native implementation is impressive, and suggests that eBPF-CCAs can possibly also be used as a long-term deployment option outside of research and development stages.
+The minor performance overhead when compared to the kernel native implementation suggests that eBPF-based CCAs can be used as a long-term deployment option outside of research and development stages.
 With regards to CCP, while the performance overhead of eBPFCCP is non-negligible, it should be noted that the benchmark is performed on a single core VM.

### 2024-12-12 paper/sections/introduction.tex
paper: revise

@@
 TCP congestion control forms a critical part of the Internet ecosystem.
-It is often an active area of research, with new algorithms being proposed to improve network performance \cite{CCA-BBR, CCA-FCC} and discussions about how CCAs influence fairness between users \cite{CCAStarvation, CCA-Fairness}.
+It is an active area of research that involves new algorithms being proposed to improve network performance \cite{CCA-BBR, CCA-FCC} and discussions about how CCAs influence fairness between users \cite{CCAStarvation, CCA-Fairness}.
 Hence, congestion control research is critical to the stable operation and continuous improvement of the Internet, even in a post-flow rate fairness era ~\cite{PrinciplesForCongestionManagement, Dismantling}.\\
@@
 \\
-With recent advancements in the eBPF space, the possibility of leveraging eBPF as a platform for implementing CCAs has emerged.
+With recent advancements in the eBPF space, the possibility of leveraging eBPF as a platform for implementing CCAs has become more apparent.
 eBPF \cite{ebpf} can be used to write and install programs that run in the Linux kernel with certain safety guarantees.
@@
 This approach has the potential to solve both the development friction and distribution difficulties of developing new CCAs.
-The eBPF verifier provides powerful guarantees to the safety of the program, protecting against large amounts of hard-to-solve bugs that lead to the kernel crashing.
+The eBPF verifier provides powerful guarantees to the safety of the program, protecting against large amounts of hard-to-solve bugs that may lead to kernel crashes.
 Furthermore, the runtime-attached nature of eBPF makes iterating and testing new versions much easier.
-On the adoption side, the safety guarantees provided by eBPF will greatly encourage user adoption.
-While users can be hesitant in installing kernel patches or modules, attaching a eBPF program can be much lower-risk and appealing.
+On the adoption side, the safety guarantees provided by eBPF would greatly encourage user adoption.
+While users can be hesitant in installing kernel patches or modules, attaching a eBPF program can be much lower-risk and thus appealing.
 \\
-Despite these upsides, running CCAs in eBPF can possibly incur extra costs due to running in the eBPF VM.
-By instrumenting the performance overheads of various different ways of implementing CCAs, this paper explores the degree to which eBPF can be used as a platform for developing CCAs.
-In addition to CCAs directly implemented using eBPF, other means of developing CCAs quickly and safely are also tested.The Congestion Control Plane (CCP) \cite{cpp}, for example, is an idea proposed to implement CCAs in user space.
-Since the original CCP kernel datapath is written as a Linux kernel module, we also implemented an alternative datapath in eBPF to potentially take advantage of the safety guarantees.
+However, running CCAs in eBPF can possibly incur extra costs due to running in the eBPF VM.
+By considering the performance overheads of various different ways of implementing CCAs, this paper explores the degree to which eBPF can be used as a platform for developing CCAs.
+In addition to CCAs directly implemented using eBPF, other means of developing CCAs quickly and safely are also tested.
 \end{document}

### 2024-12-12 paper/sections/relatedwork.tex
paper: revise

--- 2024-12-06 paper/sections/relatedwork.tex
@@
 \begin{document}
-CCP decoupled data gathering and CCA computation.
-A datapath module gathers information regarding a TCP flow and sends it to user space via various methods (such as netlink sockets and unix pipes), while a user space program listens to the given data and sends back any updates to be made to the TCP connection state.
-Platform/OS independence
+In order to fully evaluate performance of eBPF-based CCAs against alternative approaches, we looked at prior research aimed at reducing CCA-development overhead.
+Specifically, CCP \cite{ccp} was developed to be an abstraction layer where developers can experiment with new CCA ideas without worrying about the intricacies of specific datapath implementations.
+Most notably, CCP decoupled data gathering and CCA computation.
+A custom datapath module gathers TCP flow state and sends it to user space via various channels, such as netlink sockets and unix pipes.
+A user space program then listens to the provided data and sends back any updates to be made to the TCP connection state.
+Since the computation lives in user space, developers are shielded from the potential of introducing kernel-crashing bugs as long as the underlying CCP datapath implementation is safe.
+\\
+Due to CCP's datapath-reliant nature, the performance of any CCP-based congestion control algorithm will depend on the implementation of the underlying datapath, as well as the channel used to communicate between user space and kernel space.
+In our investigations to test the performance of CCP-based CCAs, we built an alternative datapath module that is implemented as an eBPF program rather than a kernel module.
+In addition to providing more safety guarantees, this implementation also allows us to test how the performance of CCP-based CCAs can vary depending on the underlying datapath implementation.
+\\
+
 \end{document}

### 2024-12-12 paper/sections/evaluation.tex
feat: added numerical metrics and changed repo link

@@
 The eBPF implementation of TCP Cubic achieved similar CPU performance compared to the built-in Linux kernel networking stack implementation.
-CCP-Cubic from the CCP Project \cite{generic-cong-avoid} combined with the CCP datapath kernel module and netlink slightly lower performance, where its median is at x percent of the full kernel implementation value.
-Our implementation of eBPFCCP ranked lower on the performance chart, but was still able to achieve y percent of the full kernel implementation value.
+CCP-Cubic from the CCP Project \cite{generic-cong-avoid} combined with the CCP datapath kernel module and netlink slightly lower performance, where its median is at 91 percent of the full kernel implementation value.
+Our implementation of eBPFCCP ranked lower on the performance chart, but was still able to achieve 80 percent of the full kernel implementation value.
 Due to the relative comparability of CPU performance between the kernel and eBPF implementations of TCP Cubicm, we theorize the gap between eBPFCCP and kernel module CCP was due to our choice of using unix pipes rather than netlink as a channel for communicating between the eBPFCCP and the user space program.

### 2024-12-12 paper/sections/evaluation.tex
chore: minor fixes

@@
 \begin{enumerate}
-    \item {\bf Behavior}: how accurate is eBPFCCP in replicating original CCA behavior?
-    \item {\bf Performance}: what is the performance overhead of eBPFCCP?
+    \item {\bf Behavior}: how accurate is an alternative implementation in replicating original CCA behavior?
+    \item {\bf Performance}: what is the performance overhead of the alternative implementation?
 \end{enumerate}
@@
 Our implementation of eBPFCCP ranked lower on the performance chart, but was still able to achieve 80 percent of the full kernel implementation value.
-Due to the relative comparability of CPU performance between the kernel and eBPF implementations of TCP Cubicm, we theorize the gap between eBPFCCP and kernel module CCP was due to our choice of using unix pipes rather than netlink as a channel for communicating between the eBPFCCP and the user space program.
+Due to the relative comparability of CPU performance between the kernel and eBPF implementations of TCP Cubic, we theorize the gap between eBPFCCP and kernel module CCP was due to our choice of using unix pipes rather than netlink as a channel for communicating between the eBPFCCP and the user space program.
 \\

### 2024-12-13 paper/sections/design.tex

@@
 
-Due to the eBPF's intense verifier requirements and stipulations, running \texttt{libccp} within the eBPF program was deemed difficult.
+Due to eBPF's intense verifier requirements and stipulations, running \texttt{libccp} within the eBPF program was deemed difficult.
 Consequently, we create a user space layer between the CCP agent and the Linux kernel's TCP stack, called eBPFCCP.
@@
 eBPFCCP's role is to collect primitive congestion signals from the eBPF program, send them over to the CCP agent, and execute instructions sent by the CCP agent to influence TCP behavior.
-As shown in Figure~\ref{fig:ebpfccp}, eBPFCCP communicates with the CCP agent via Unix-domain sockets and interfaces with the eBPF datapath program using BPF hash maps and BPF ring buffers.
+As shown in Figure~\ref{fig:ebpfccp}, eBPFCCP communicates with the CCP agent via Unix-domain sockets as its IPC mechanism and interfaces with the eBPF datapath program through BPF hash maps and BPF ring buffers.
 
@@
 This signals eBPFCCP to retrieve the new flow's information and pass it to the CCP agent.
-Similarly, when a flow is terminated, the eBPF datapath program writes an event to the \texttt{free\_conn\_events} ring buffer, which eBPFCCP reads to perform flow cleanup actions.
+Similarly, when a flow is terminated, the eBPF datapath program writes an event to the \texttt{free\_conn\_events} ring buffer, which eBPFCCP then reads to perform flow cleanup actions.
 As new ACKs arrive, the eBPF datapath program reads the TCP state and calculates primitive congestion signals, which are then written to the \texttt{signals} ring buffer, read by eBPFCCP, and sent to the CCP agent.
-Then, the message the CCP agent sends back to the eBPFCCP pertaining to window size and pacing rate is written to the \texttt{connections} hash map, which the eBPF datapath program reads and updates the TCP state accordingly.
+Then, messages pertaining to congestion window size and sending rate are written to the \texttt{connections} hash map.
 The BPF maps used by the eBPF datapath and eBPFCCP are summarized in Table~\ref{tab:maptable}.
@@
 
-Overall, the eBPFCCP aims to act as a bridge between the CCP agent and the eBPF datapath program.
+Overall, eBPFCCP aims to act as a bridge between the CCP agent and the eBPF datapath program.
 

### 2024-12-13 paper/sections/introduction.tex

@@
 \begin{enumerate}
-    \item {\bf Development friction}: CCA implements are often split between different datapaths.
+    \item {\bf Development friction}: CCA implementations are often split between different datapaths.
 In the Linux kernel, this involves writing kernel code or modules, which presents a high barrier of entry and is prone to bugs that can crash the system.
-    \item {\bf Distribution difficulties}: Pushing a new CCA upstream to the Linux kernel is difficult.
+    \item {\bf Distribution difficulties}: Pushing a new CCA upstream to the Linux kernel is difficult due to rigorous review processes and backward compatibility concerns.
 To see real-world adoption, a new CCA must be user-friendly and easy to adopt in the early stages.

### 2024-12-13 paper/main.tex
small fix
paper: revise
paper: fix title

@@
   howpublished =         {\url{https://iperf.fr/}},
-  notenote = {Accessed: 2024-11-12}
+  note = {Accessed: 2024-11-12}
 }
@@
 % make title bold and 14 pt font (Latex default is non-bold, 16 pt)
-\title{\Large \bf Evaluating eBPF as a Platform for Congestion Control Algorithm}
+\title{\Large \bf Evaluating eBPF as a Platform for Congestion Control Algorithm Implementation}
 
@@
 
-We would like to thank Brown's CS2680 and Professor Akshay Narayan for the help provided in the development of this project.
-The source code for all the artifacts (eBPF-Cubic, eBPFCCP, benchmark suite) is available at \url{https://github.com/claby2/ebpfcca}
+We would like to thank Brown's CS2680 and Professor Akshay Narayan for the help provided in the development of this project. The source code is available at: \\
+\url{https://github.com/ebpfcca/ebpfcca}
 
